We analyse the stellar and dark matter distribution in the spiral galaxy SDSS J1331+3638 (J1331) by means of two independent methods: gravitational lensing and dynamical Jeans modelling. Hubble Space Telescope (HST) imaging by \citet{SWELLSI} reveals, that J1331's bulge is superimposed by a quadruplet of extended lensing images. By fitting a gravitational potential model to the image positions, we constrain the mass inside the Einstein radius ($R_\text{ein}=0.91\pm0.02$ arcsec) to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$). From Multi-Gaussian Expansions (MGE) of J1331's surface brightness distribution we find that J1331 has a total I-band luminosity of $L_{I,tot} \simeq 5.6 \cdot 10^{10}L_{I,\odot}$ and an effective radius of $R_\text{eff} \simeq 2.6$ arcsec = 5.6 kpc. [TO DO: I guess, apparent magnitude is not very interesting.]

According to the long-slit major axis stellar kinematics from \citet{SWELLSV}, J1331 has a counter-rotating stellar core inside $\sim 2$ arcsec. We model the observed stellar kinematics in J1331's central regions by finding MGE models for the surface brightness, stellar and dark matter distribution that solve the axisymmetric Jeans equations. We test galaxy models for (A) mass-follows-light with velocity anisotropy, (B) an increasing mass-to-light ration gradient, (C) the best fit lens model, and (D) including an NFW dark matter halo. We show that, because model (A) fails to reproduce the observed kinematics, J1331 requires a steep total mass-to-light ratio gradient in the center. Model (B) predicts independently the same total mass inside the Einstein radius as the lens model, and vice versa model (C) gives an independent prediction of the observed kinematics in the galaxy center. We constrain the NFW halo of J1331 in model (D) to have a virial velocity $v_{200} \simeq 240 \pm 40$ km/s and a concentration of $c_{200} \simeq 8 \pm 2$ in case of a moderate tangential velocity anisotropy of $\beta_z \simeq −0.4 \pm 0.1$. The NFW halo models can successfully reproduce the signatures of J1331's counter-rotating stellar core and predict J1331's rotation curve at larger radii. However, all these models were more massive than expected from the gas rotation curve at larger radii, and failed to reproduce the steep drop in measured velocity dispersion at [TO DO: WHAT RADIUS???]. This could indicate a non-trivial re-distribution of matter due a possible minor merger event in J1331's past.

[TO DO: something about mass to light ratios????]