\section{Data} \label{sec:data}

\paragraph{Redshift and position.} J1331 is located at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000). \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}. According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.

\paragraph{HST imaging.} We use HST imaging of J1331 by \citet{SWELLSI}. They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip. The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$. In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness MGE model of the reddish bulge.

\paragraph{Stellar kinematics.} For the dynamical modelling we use the stellar kinematics for J1331 measured by \citet{SWELLSV}. They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope. The width of the slot was $1''$ and the seeing conditions had a FWHM of $\sim 1.1''$. Spectra for spatial bins of different widths along the major axis were extracted. They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission \Wilma{[TO DO: Check if really emission lines or, more likely, absorption lines]} lines in these spectra \Wilma{[TO DO: Find out which lines]}. Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for ionized gas.
\\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}. The rotation curve reveals a counter-rotating core within $2''\simeq$ 4 kpc. Outside of $\sim 3.5''$ there is a steep drop in the dispersion, which is expected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}. However, in the brighter F814W filter in Figure \ref{fig:F814W}  the large reddish bulge extends out to $\sim5''$. 
\\Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data. We add $-2.3~\text{km s}^{-1}$ to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity. We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data. In the JAM modelling, which is based on the assumption of axisymmetry, only stellar kinematics with $R'  \lesssim 2.5''$ or $R' \lesssim 4''$ are used. Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.

 \Wilma{[TO DO: Maybe mention the following details better in the data section.... "Sufficiently inclined galaxies were picked by eye. Follow-up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}."]}